Methods for Projecting Population Growth

### 2018-05-02 final/tex/Paper.tex
Additional updates

\documentclass{article}
\usepackage{authblk}
\usepackage{mathptmx}
\usepackage{url,latexsym,amsmath,amsthm,xspace,rotating,multirow,multicol,xspace,amssymb,paralist}
\usepackage{euscript}
\usepackage{fancybox,xcolor}
\usepackage{longtable}
\usepackage{paralist}
\usepackage[normalem]{ulem}
\usepackage[pdftex]{hyperref}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{cancel}
\usepackage{mathtools}

@@

>>>>

\documentclass{article}
\usepackage[title]{appendix}
\usepackage{authblk}
\usepackage{mathptmx}
\usepackage{url,latexsym,amsmath,amsthm,xspace,rotating,multirow,multicol,xspace,amssymb,paralist}
\usepackage{euscript}
\usepackage{fancybox,xcolor}
\usepackage{longtable}
\usepackage{paralist}
\usepackage[normalem]{ulem}
\usepackage[pdftex]{hyperref}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{cancel}
\usepackage{mathtools}

@@

\subsection{Additional Simulation}

\todo{Complete Jupyter simulations}

\subsection{Analysis}

\todo{Analyze results}

\begin{appendices}
\section{Simulation Code}
\todo{Insert actual code with comments}

\begin{lstlisting}[language=Python]
def model(params):   
    a1, a3k1, a2, b1, b2 = params
    # Sample comment
    def dpdt(x, t):
        return (a1*x[0] + a3k1*x[1] + a2*x[0]*x[1])
    def dgdt(x, t):
        return b1*x[1] + b2*x[0]*x[1]
    def dxdt(x, t):
        return np.array([dpdt(x, t),  dgdt(x, t)])

    x0 = [1.15e9, 0.21e12]
    t = np.arange(1850, 2150, 1)
    return integrate.odeint(dxdt, x0, t)
\end{lstlisting}

\end{appendices}
